Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Text wrapping
Text wrapping; can't fix exponential labels

\caption{\hl {Reynolds} number dependence of the normalized peak torque coefficient
 calculated from static foil coefficients and blade kinematics, compared to
 experimental data from a cross-flow turbine. Note that the experimental data
 represents the mean torque coefficient, not the maximum.}
 %please pay attention to the value ``1e5'' in the figure. is it ``\times 10^5''. If yes, please revise it to \times 10 ^5 in the figure. meanwhile, is it better to make different color with the lines?

>>>>

    \caption{Reynolds number dependence of the normalized peak torque
        coefficient calculated from static foil coefficients and blade kinematics,
        compared to experimental data from a cross-flow turbine. Note that the
        experimental data represents the mean torque coefficient, not the maximum.}
